Simulating High-Dimensional Multivariate Data

### 2020-12-29 030-bigsimr-package.Rmd
Begin rewriting after moving to bigsimr develop branch

```{r ch030-cor-convert, echo=TRUE}
## Step 1. Mapping
(R_X <- cor_convert(rho = R_S, from = type, to = 'pearson'))
## Step 2. Check admissibily
is_valid_correlation <- function(rho) {
  all(diag(rho) == 1) && matrixcalc::is.positive.semi.definite(rho)
}
is_valid_correlation( R_X )
matrixcalc::is.symmetric.matrix( R_X )
all(diag(R_X) == 1)
cor_nearPSD( G = R_X )
```

@@

```{r ch030-cor-bounds-pearson, echo=TRUE}
cor_bounds(margins = margins, type = 'pearson', reps = 1e5)
```

@@

```{r ch030-sim-margins, echo=TRUE}
x <- rvec(10000, R_S, margins, type)
df_sim <- as.data.frame(x)
colnames(df_sim) <- colnames(df)
```

>>>>

```{r ch030-cor-convert, echo=TRUE}
## Step 1. Mapping
(R_X <- cor_convert(rho = R_S, from = type, to = 'pearson'))
## Step 2. Check admissibily
is_valid_correlation <- function(rho) {
  all(diag(rho) == 1) && matrixcalc::is.positive.semi.definite(rho)
}
is_valid_correlation( R_X )
```

@@

```{r ch030-cor-bounds-pearson, echo=TRUE}
cor_bounds(margins = margins, method = 'pearson', reps = 1e5)
```

@@

```{r ch030-sim-margins, echo=TRUE}
x <- rvec(n = 10000, rho = R_X, margins)
df_sim <- as.data.frame(x)
colnames(df_sim) <- colnames(df)
```

### 2020-12-29 index.Rmd
Begin rewriting after moving to bigsimr develop branch

```{r indexSetup, echo = FALSE, eval = TRUE, message=FALSE, warning=FALSE, results = "hide", cache=F}
library(tidyverse)
library(knitr)
knitr::opts_chunk$set(eval = TRUE, echo = FALSE, cache = TRUE)
library(rmarkdown)
library(bookdown)
## setwd('~/article_bigsimr')
set.seed(09212020)
```

>>>>

```{r indexSetup, echo = FALSE, eval = TRUE, message=FALSE, warning=FALSE, results = "hide", cache=F}
library(bigsimr)
library(tidyverse)
library(knitr)
knitr::opts_chunk$set(eval = TRUE, echo = FALSE, cache = TRUE)
library(rmarkdown)
library(bookdown)
## setwd('~/article_bigsimr')
set.seed(09212020)
```
